A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-06-22 03_Prep_data.Rmd
Replace "Lets" with "Let's"

```{r load_libraries, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, agricolae, lme4, here
)
```

@@

We are narrowing the meta-analysis to only include treatments using demethylation inhibitors, tebuconazole and propiconazole. 
Lets look at what type of statistical error was reported for the trials that used these fungicides.

```{r variance_types}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref, location,year ,Y_error_type, fungicide_ai) %>%
   summarise(DMI_treatments = length(Y_error_type)) %>%
   arrange(Y_error_type) %>%
   select(!fungicide_ai)%>%
   kable(caption = "Number of treatments for each trial and the error type reported", align = "c") %>%
   footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
```

@@

First lets get a list the of trials that reported LSD.  
```{r all_LSD_trials}
Trials <- PM_MB_means %>%
   filter(Y_error_type == "lsd (P=0.05)") %>%
   select(trial_ref) %>%
   distinct()
Trials
```
Lets use this list of trials to subset the data and calculate sampling variances.

@@

Earlier we noted there were different doses of propiconazole which might influence our analysis. 
Lets check this by comparing a linear mixed effect model including and excluding dose. 
We already have a factor breaking down the dose in the `trial` variable, lets make a new one without dose.

@@

Lets test the dose effect in a basic linear mixed effect model

@@

Lets have a quick look to examine whether trials with high disease pressure sustain a greater yield loss.

@@

We may want to consider row spacing in the trials, However one of the locations has NA as the row spacing. 
For now lets assign the most used row spacing of 0.33
```{r}
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33

>>>>

```{r load_libraries, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, agricolae, lme4, here)
```

@@

We are narrowing the meta-analysis to only include treatments using demethylation inhibitors, tebuconazole and propiconazole.
Let's look at what type of statistical error was reported for the trials that used these fungicides.

```{r variance_types}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref, location, year , Y_error_type, fungicide_ai) %>%
   summarise(DMI_treatments = length(Y_error_type)) %>%
   arrange(Y_error_type) %>%
   select(!fungicide_ai) %>%
   kable(caption = "Number of treatments for each trial and the error type reported", align = "c") %>%
   footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
```

@@

First Let's get a list the of trials that reported LSD.

```{r all_LSD_trials}
Trials <- PM_MB_means %>%
   filter(Y_error_type == "lsd (P=0.05)") %>%
   select(trial_ref) %>%
   distinct()
Trials
```
Let's use this list of trials to subset the data and calculate sampling variances.

@@

Earlier we noted there were different doses of propiconazole which might influence our analysis. 
Let's check this by comparing a linear mixed effect model including and excluding dose. 
We already have a factor breaking down the dose in the `trial` variable, Let's make a new one without dose.

@@

Let's test the dose effect in a basic linear mixed effect model

@@

Let's have a quick look to examine whether trials with high disease pressure sustain a greater yield loss.

@@

We may want to consider row spacing in the trials, However one of the locations has NA as the row spacing. 
For now Let's assign the most used row spacing of 0.33
```{r}
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33
